Hydra Battles and Cie

### 2021-03-05 doc/part-hydras.tex
add new exercise
new exercise
improved an exercise

\begin{exercise}
Let us quote a theorem from ~\cite{KS81} (page 297).

>>>>

\index{hydras}{Exercises}
\begin{exercise}

Prove that for any $n\geq 2$, $\textrm{Ack}\,\,n\,n\leq  F_\omega(n)$, where \textrm{Ack} is the Ackermann function. Next, prove that $F_\alpha$ is not primitive recursive, for any $\alpha\geq\omega$  (please see Sect.~\vref{sect:ack-not-PR}).
On the other hand, please show that for any natural number $n$, the function $F_n$ is primitive recursive.

\emph{You may start this exercise with the file
\url{../exercises/ordinals/F_omega.v}. Properties of the Ackermann function are studied in 
\url{../theories/ordinals/MoreAck/Ack.v} and
\url{../theories/ordinals/MoreAck/AcknotPR.v}.}
\end{exercise}

\index{hydras}{Exercises}
\begin{exercise}
Let us quote a theorem from ~\cite{KS81} (page 297).
